Visually pleasing knot projections

### 2021-09-24 inst/jma_rebuttal.tex

P2, line 46: What does it mean for symmetry to be ``present" in the
knot?

\textcolor{blue}{
  \begin{description}
  \item[OLD text] Any symmetry present in the knot should be enforced exactly, and be visually apparent
\item[NEW text] Any symmetry desired in the knot should be enforced exactly, and be visually apparent
  \end{description}
}

P3, line 31: Define ``visual continuity".  Are you referring to tangent
continuity, $G1-$, or $G2-$ continuity?

\textcolor{blue}{%--------------------------------------------issue22
  The path does not have G2 continuity because the radius of curvature
  has a discontiniuity at Bezier nodes.  But the change of curvature
  should be small, I have added a short discussion to clarify the
  issue.}

@@

Figure 2:  Specify what order Bezier curves are being used.

\textcolor{blue}{fixed}%issue#24

P4, line 18: A gentle introduction to ``R" would help to make the
following easier to understand.

\textcolor{blue}{Fixed, a short introductory passage and a reference
  to R core now added}%issue#25

### 2021-09-24 inst/jma_knot.tex
fixes #25

In this section, I give workflows for creating two simple knots:
firstly~$7_6$, followed by the figure-of-eight knot~$4_1$ which
requires imposition of symmetry constraints.

>>>>

The software presented here is written in the ``R'' programming
language~\cite{rcore2021}, which is usually associated with
statistical analysis and data processing.  However, R possesses a
number of features such as object-oriented programming and
high-dimensional optimization which make it suitable for producing
knot diagrams.  In this section, I give workflows for creating two
simple knots: firstly~$7_6$, followed by the figure-of-eight
knot~$4_1$ which requires imposition of symmetry constraints.
